### 2024-05-23 getting-started.qmd
20240522 - rosters
20240522 - fix error
20240522 - duplicate section identifier
20240523 - add data and data dictionaries

@@

@@

To download play-by-play data from prior weeks and seasons, we can use the `load_pbp()` function of the `nflreadr` package.
We add a progress bar using the `with_progress()` function from the `progressr` package because it takes a while to run.

@@

@@

We can download historical week-by-week actual player statistics using the `load_player_stats()` function from the `nflreadr` package:

@@

>>>>

### Players {#sec-downloadPlayers}

nfl_players <- progressr::with_progress(
  nflreadr::load_players())
```

save(
  nfl_players,
  file = here("data", "nfl_players.RData")
)
```

load(file = here("data", "nfl_players.RData"))
```

### Teams {#sec-downloadTeams}

nfl_teams <- progressr::with_progress(
  nflreadr::load_teams(current = TRUE))
```

save(
  nfl_teams,
  file = here("data", "nfl_teams.RData")
)
```

load(file = here("data", "nfl_teams.RData"))
```

@@

### Rosters {#sec-downloadRosters}

A Data Dictionary for rosters is located at the following link: <https://nflreadr.nflverse.com/articles/dictionary_rosters.html>

nfl_rosters <- progressr::with_progress(
  nflreadr::load_rosters(seasons = TRUE))

nfl_rosters_weekly <- progressr::with_progress(
  nflreadr::load_rosters_weekly(seasons = TRUE))
```

save(
  nfl_rosters,
  file = here("data", "nfl_rosters.RData")
)

save(
  nfl_rosters_weekly,
  file = here("data", "nfl_rosters_weekly.RData")
)
```

load(file = here("data", "nfl_rosters.RData"))
load(file = here("data", "nfl_rosters_weekly.RData"))
```

@@

To download play-by-play data from prior weeks and seasons, we can use the `load_pbp()` function of the `nflreadr` package.
We add a progress bar using the `with_progress()` function from the `progressr` package because it takes a while to run.
A Data Dictionary for the play-by-play data is located at the following link: <https://nflreadr.nflverse.com/articles/dictionary_pbp.html>

@@

load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_pbp.RData", fsep = ""))
```

### Participation {#sec-downloadParticipation}

A Data Dictionary for the participation data is located at the following link: <https://nflreadr.nflverse.com/articles/dictionary_participation.html>

```{r}
nfl_participation <- progressr::with_progress(
  nflreadr::load_participation(
    seasons = TRUE,
    include_pbp = TRUE))
```

save(
  nfl_participation,
  file = here("data", "nfl_participation.RData")
)
```

load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/nfl_participation.RData", fsep = ""))
```

@@

We can download historical week-by-week actual player statistics using the `load_player_stats()` function from the `nflreadr` package.
A Data Dictionary for statistics for offensive players is located at the following link: <https://nflreadr.nflverse.com/articles/dictionary_player_stats.html>.
A Data Dictionary for statistics for defensive players is located at the following link: <https://nflreadr.nflverse.com/articles/dictionary_player_stats_def.html>.

@@

## Data Dictionary {#sec-dataDictionary}

Data Dictionaries are metadata that describe the meaning of the variables in a datset.
You can find Data Dictionaries for the various NFL datasets at the following link: <https://nflreadr.nflverse.com/articles/index.html>.
